Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-04-28 files/Chapter2/generalvibrationmodel.tex
Saving model

Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions as given in \cite{CVV18}:
\begin{flalign}
	T_n(t) &= e^{-r_nt}\left[ A_n \cos(\omega_n t) + B_n \sin(\omega_n t) \right] \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
	T_n(t) &= e^{-r_nt}\left[ A_n + B_n t \right] \quad \textrm{ if } \lambda = 0, \label{lambda_2}\\
	T_n(t) &= e^{-r_nt}\left[ A_n \cosh(\mu_n t) + B_n \sinh(\mu_n t) \right] \quad \textrm{ if } \lambda < 0. \label{lambda_3}
\end{flalign}

From assumptions \textbf{A2} and \textbf{A3}, the bilinear forms $b$ and $c$ are positive definite. And since we assumed that there is no damping ($a=0$), $\lambda$ cannot be negative. Therefore, the only possible solutions for $T_n(t)$ is \eqref{lambda_1} and \eqref{lambda_2}.

>>>>

Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions:
\begin{flalign}
	T_n(t) &=  A_n \cos(\omega_n t) + B_n \sin(\omega_n t) \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda = 0, \label{lambda_2}\\
	T_n(t) &=  A_n \cosh(\mu_n t) + B_n \sinh(\mu_n t) \quad \textrm{ if } \lambda < 0. \label{lambda_3}
\end{flalign}
